### 2016-06-25 writing/pppresentation/wilf.tex
PP presentation

\section{Wilf-equivalences}
\label{sec:Wilf-equivalences}
\subsection{Wilf-equivalence}
\label{sub:Wilf-equivalence}
\begin{frame}{Wilf-equivalence}
  \begin{definition}
  Two patterns are said to be \emph{Wilf-equivalent} if the set of avoiders
  of the patterns is the same size at every length.
\end{definition}
 All coincident pattern classes are Wilf-equivalent.

 The permutations in \(\av{\perm{2,3,1}}\) of length \(n\) are counted by the
 Catalan numbers.
 \begin{equation}
   C_0 = 1, \text{ and } C_{n+1} =\sum_{i=0}^{n}C_iC_{n-i}
 \end{equation}
 This gives the sequence
 \begin{equation*}
   1,1,2,5,14,42,132,1430,4862,\dotsc
 \end{equation*}
\end{frame}
\subsection{Set Partitions}
\label{sub:Set Partitions}
\begin{frame}{Set Partitions}
  \begin{block}{Note}
    The avoiders of the pattern \(q = \mperm{2,3,1}{\{(1,0),(1,1),(1,2),(1,3)\}}\),
    \textpattern{}{2,3,1}{1/0,1/1,1/2,1/3},
    in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions of
    \(\nrange{n}\). (Claesson \cite{A})
\end{block}
\begin{example}
    Given the permutation \(\pi = \perm{5,4,2,1,3,9,6,8,7}\) this corresponds to the
    partition \(\{\{5,4,2,1\},\{3\},\{9,6\},\{8,7\}\}\).
\end{example}
All permutations in \(\av{\perm{2,3,1}}\) are also in \(\av{q}\).
\end{frame}
\begin{frame}
  Set Partitions can be used to explain certain Wilf-equivalences.
  \begin{example}
    The following patterns are experimentally Wilf-equivalent up to length 10 in
\(\av{\perm{2,3,1}}\)
  \begin{equation*}
      m_1 = \pattern{}{1,2}{0/0,0/2,
                      1/0,1/1,
                      2/0,2/1,2/2}
      \text{ and }
      m_2 = \pattern{}{1,2}{0/0,
                      1/0,1/1,1/2,
                      2/0,2/1,2/2}
  \end{equation*}
  Consider containers of the patterns in \(\av{\perm{2,3,1}}\).

@@

\end{frame}
\subsection{Generating Functions}
\label{sub:Generating Functions}
\begin{frame}{Generating {\huge FUN}ctions}
  \begin{block}{}
    \blockquote[Herbert Wilf, \emph{generatingfunctionology}~\cite{Wilf}]{%
    A generating function is a clothesline on which we hang up a sequence of numbers for display.}
    % \flushright -Herbert Wilf, \emph{generatingfunctionology}
  \end{block}
  \begin{definition}
    The \emph{ordinary generating function (OGF)} of a sequence \((A_n)\) is the
    formal power series
    \begin{equation}
      A(x) = \sum_{n=0}^{\infty} A_nx^n
    \end{equation}
    The right hand side is the Taylor expansion of the left hand side at \(0\).
  \end{definition}
\end{frame}
\begin{frame}
  \begin{example}
    The generating function for the constant sequence \(\{1,1,1,1,\dotsc\}\) is
    \begin{equation*}
      f(x) = \frac{1}{1-x}
    \end{equation*}
  \end{example}
\end{frame}
\begin{frame}
  \begin{example}
  The generating function for the avoiders of the permutation \(\perm{2,3,1}\)
  satisfies
  \begin{equation}
    C(x) = 1 +xC^2(x)
  \end{equation}
  This can be seen structurally (\(\mathcal{C}\) is the set of \(\perm{2,3,1}\) avoiders)
  \begin{figure}[!ht]
    \centering
    \(\mathcal{C} = \varepsilon \mathrel{\sqcup}\) \decompmax{0/1,1/0}{\only<1>A\only<2->{\mathcal{C}}}{}{}{\only<1>B\only<2->{\mathcal{C}}}
\end{figure}
\only<3->{
Solving for \(C(x)\) and taking the Taylor expansion at \(0\) gives
\begin{equation*}
  1+x+2x^2+5x^3+14x^4+42x^5+132x^6+1430x^7+4862x^8+\dotsb
\end{equation*}
}

\end{example}
\end{frame}
\begin{frame}
  Now we consider one of the Wilf-equivalences between mesh patterns in \(\av{\perm{2,3,1}}\).
  \begin{equation*}
    m_1 = \pattern{}{1,2}{1/0,1/1,1/2,2/0,2/1} \text{ and }
    m_2 = \pattern{}{2,1}{0/1,1/0,1/1,1/2,2/1}
  \end{equation*}
\end{frame}

>>>>

\section{Wilf-equivalences}
\label{sec:Wilf-equivalences}
\subsection{Wilf-equivalence}
\label{sub:Wilf-equivalence}
\begin{frame}{Wilf-equivalence}
%   \begin{definition}
%   Two patterns are said to be \emph{Wilf-equivalent} if the set of avoiders
%   of the patterns is the same size at every length.
% \end{definition}
 All coincident pattern classes are Wilf-equivalent.

 We Wilf-classify classes of the form \(\av{231,m}\) where \(m\)
 is a mesh pattern.

 % The permutations in \(\av{\perm{2,3,1}}\) of length \(n\) are counted by the
 % Catalan numbers.
 % \begin{equation}
 %   C_0 = 1, \text{ and } C_{n+1} =\sum_{i=0}^{n}C_iC_{n-i}
 % \end{equation}
 % This gives the sequence
 % \begin{equation*}
 %   1,1,2,5,14,42,132,1430,4862,\dotsc
 % \end{equation*}
\end{frame}
\subsection{Set Partitions}
\label{sub:Set Partitions}
\begin{frame}{Set Partitions}
  \begin{block}{Note}
    The avoiders of the pattern \(q = \mperm{2,3,1}{\{(1,0),(1,1),(1,2),(1,3)\}}\),
    \textpattern{}{2,3,1}{1/0,1/1,1/2,1/3},
    in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions of
    \(\nrange{n}\). (Claesson \cite{A})
\end{block}
\begin{example}
    Given the permutation \(\pi = \perm{5,4,2,1,3,9,6,8,7}\) this corresponds to the
    partition \(\{\{5,4,2,1\},\{3\},\{9,6\},\{8,7\}\}\).
\end{example}
All permutations in \(\av{\perm{2,3,1}}\) are also in \(\av{q}\).
\end{frame}
\begin{frame}
  Set Partitions can be used to explain certain Wilf-equivalences.
  \begin{example}
    The following patterns are experimentally Wilf-equivalent up to length 10 in
\(\av{\perm{2,3,1}}\)
  \begin{equation*}
      m_1 = \pattern{}{1,2}{0/0,0/2,
                      1/0,1/1,
                      2/0,2/1,2/2}
      \text{ and }
      m_2 = \pattern{}{1,2}{0/0,
                      1/0,1/1,1/2,
                      2/0,2/1,2/2}
  \end{equation*}
  Consider containers of the patterns in \(\av{\perm{2,3,1}}\).

@@

\end{frame}
\subsection{Generating Functions}
\label{sub:Generating Functions}
% \begin{frame}{Generating {\huge FUN}ctions}
%   \begin{block}{}
%     \blockquote[Herbert Wilf, \emph{generatingfunctionology}~\cite{Wilf}]{%
%     A generating function is a clothesline on which we hang up a sequence of numbers for display.}
%     % \flushright -Herbert Wilf, \emph{generatingfunctionology}
%   \end{block}
%   \begin{definition}
%     The \emph{ordinary generating function (OGF)} of a sequence \((A_n)\) is the
%     formal power series
%     \begin{equation}
%       A(x) = \sum_{n=0}^{\infty} A_nx^n
%     \end{equation}
%     The right hand side is the Taylor expansion of the left hand side at \(0\).
%   \end{definition}
% \end{frame}
% \begin{frame}
%   \begin{example}
%     The generating function for the constant sequence \(\{1,1,1,1,\dotsc\}\) is
%     \begin{equation*}
%       f(x) = \frac{1}{1-x}
%     \end{equation*}
%   \end{example}
% \end{frame}
\begin{frame}{Generating Functions by Structure}
  \begin{example}
  The generating function for the avoiders of the permutation \(\perm{2,3,1}\)
  satisfies
  \begin{equation}
    C(x) = 1 +xC^2(x)
  \end{equation}
  This can be seen structurally (\(\mathcal{C}\) is the set of \(\perm{2,3,1}\) avoiders)
  \begin{figure}[!ht]
    \centering
    \(\mathcal{C} = \varepsilon \mathrel{\sqcup}\) \decompleft{0/1,1/0}{{\mathcal{C}}}{}{}{{\mathcal{C}}}
\end{figure}
% \only<2->{
% Solving for \(C(x)\) and taking the Taylor expansion at \(0\) gives
% \begin{equation*}
%   1+x+2x^2+5x^3+14x^4+42x^5+132x^6+1430x^7+4862x^8+\dotsb
% \end{equation*}
% }
%
\end{example}
\end{frame}
\begin{frame}
  Now we consider one of the Wilf-equivalences between mesh patterns in \(\av{\perm{2,3,1}}\).
  \begin{equation*}
    m_1 = \pattern{}{1,2}{1/0,1/1,1/2,2/0,2/1} \text{ and }
    m_2 = \pattern{}{2,1}{0/1,1/0,1/1,1/2,2/1}
  \end{equation*}
\end{frame}
